Fifteen years of decentralization attempts

### 2014-03-24 paper.tex
Move tables down the page to avoid whitespace
Sentence fix

		In the table we notice that three of the entries are privacy enhancing networks that aim to provide unlinkability (Freenet, Tor, GNUnet), plus one that is currently in the process of implementing such a feature (Tribler). Furthermore we notice that, once above a certain threshold, none of the statistics have a clear effect on a projects popularity. For example, Freenet and Tor have similar statistics, while the number of Tor users \cite{tormetricsprojectwebsite} is several orders of magnitude higher than Freenet \cite{freenetstatistics}.

>>>>

		In the table we notice that three of the entries are privacy enhancing networks that aim to provide unlinkability (Freenet, Tor, GNUnet), plus one that is currently in the process of implementing such a feature (Tribler). Furthermore we notice that, once above a certain threshold, none of the statistics have a clear effect on a projects popularity. For example, Freenet and Tor have similar statistics, while the number of Tor users \cite{tormetricsprojectwebsite} is several orders of magnitude higher than the number of Freenet users \cite{freenetstatistics}.
